### 2020-03-04 submission/manuscript.Rmd
Grammar edits

It is critical that the presenter and participants respect each other and that there be an individual (e.g. the lab director) that enforces a code of conduct. Everyone in the session needs to have the humility to acknowledge that they still have more to learn about any topic. We have found that many problems are avoided when the presenter takes charge of the session by having a clear lesson plan, thoughtfully creates groups, and gives encouragement. Similarly, participants foster a positive environment by remembering that the task is not a competition, focusing on the presenter's goals, allowing their partner to contribute, asking clarifying questions when appropriate, and avoiding distractions (e.g. email, social media). Learning to program is challenging and too often it can lead to a toxic environment. All parties in a Code Club are responsible for preventing this toxicity.

@@

In our early Code Clubs we noticed that if the presenter did not clearly state their goals for the session, it would often led to frustration for the presenter and participants. If the presenter shared their own code, did they want us to focus on their coding style or do they want help with incorporating a new package into their workflow? Participants will always notice or ask about things that are not the focus of the exercise. Be specific about the goal and bring them back to the task if they are distracted. Where possible, create a simplified scenario (i.e. minimal, reproducible example [@StackOverflow_MREE]) can be helpful that removes distractions. The presenter should make sure that the simplified example works and behaves the way they expect before coming to the Code Club. Beyond the content, participants should know what they can be expected to have completed by the end of the session.

@@

Our Code Club needs to fit within an hour slot. The presenter should anticipate enough time for an introduction and brief instruction, time for participants to engage the material, and time for everyone to report back. A typical schedule for Code Review is 10 minutes of introduction and instruction, 30 minutes of paired programming, 5 minutes to get groups to wrap up, and 10 minutes to report back to the group. Remember that a task that you can accomplish in 10 minutes may take a more junior member of your group 30 minutes. The goal of the Code Club should be to help that junior member to learn the topic and to reinforce the topic for the more senior person and help them see the concept in a new context. One possibility would be to create "stretch goals" for those that complete the task more quickly than everyone else. We once had a presenter try to teach the group some basic Julia syntax. By the time people installed the interpreter, the time was up. Alternatively, a session where participants were asked to make code DRY gave them multiple stopping points where they could feel successful (e.g. commenting code, creating function, implementing function, refactoring function).

>>>>

It is critical that the presenter and participants respect each other and that there be an individual (e.g. the lab director) who enforces a code of conduct. Everyone in the session needs to have the humility to acknowledge that they still have more to learn about any topic. We have found that many problems are avoided when the presenter takes charge of the session by having a clear lesson plan, thoughtfully creating groups, and giving encouragement. Similarly, participants foster a positive environment by remembering that the task is not a competition, focusing on the presenter's goals, allowing their partner to contribute, asking clarifying questions when appropriate, and avoiding distractions (e.g. email, social media). Learning to program is challenging and too often it can lead to a toxic environment. All parties in a Code Club are responsible for preventing this toxicity.

@@

In our early Code Clubs we noticed that if the presenter did not clearly state their goals for the session, it would often led to frustration for the presenter and participants. If the presenter shared their own code, did they want us to focus on their coding style or do they want help with incorporating a new package into their workflow? Participants will always notice or ask about things that are not the focus of the exercise. Be specific about the goal and bring them back to the task if they are distracted. Where possible, creating a simplified scenario (i.e. minimal, reproducible example [@StackOverflow_MREE]) can be helpful to remove distractions. The presenter should make sure that the simplified example works and behaves the way they expect before coming to the Code Club. Beyond the content, participants should know what they can be expected to have completed by the end of the session.

@@

Our Code Club needs to fit within an hour time slot. The presenter should anticipate enough time for an introduction and brief instruction, time for participants to engage the material, and time for everyone to report back. A typical schedule for Code Review is 10 minutes of introduction and instruction, 30 minutes of paired programming, 5 minutes to get groups to wrap up, and 10 minutes to report back to the group. Remember that a task that you can accomplish in 10 minutes may take a more junior member of your group 30 minutes. The goal of the Code Club should be to help that junior member to learn the topic and to reinforce the topic for the more senior person and help them see the concept in a new context. One possibility would be to create "stretch goals" for those that complete the task more quickly than everyone else. We once had a presenter try to teach the group some basic Julia syntax. By the time people installed the interpreter, the time was up. Alternatively, a session where participants were asked to make code DRY gave them multiple stopping points where they could feel successful (e.g. commenting code, creating function, implementing function, refactoring function).

### 2020-03-04 submission/manuscript.tex
Grammar edits

It is critical that the presenter and participants respect each other
and that there be an individual (e.g.~the lab director) that enforces a
code of conduct. Everyone in the session needs to have the humility to
acknowledge that they still have more to learn about any topic. We have
found that many problems are avoided when the presenter takes charge of
the session by having a clear lesson plan, thoughtfully creates groups,
and gives encouragement. Similarly, participants foster a positive
environment by remembering that the task is not a competition, focusing
on the presenter's goals, allowing their partner to contribute, asking
clarifying questions when appropriate, and avoiding distractions
(e.g.~email, social media). Learning to program is challenging and too
often it can lead to a toxic environment. All parties in a Code Club are
responsible for preventing this toxicity.

@@

In our early Code Clubs we noticed that if the presenter did not clearly
state their goals for the session, it would often led to frustration for
the presenter and participants. If the presenter shared their own code,
did they want us to focus on their coding style or do they want help
with incorporating a new package into their workflow? Participants will
always notice or ask about things that are not the focus of the
exercise. Be specific about the goal and bring them back to the task if
they are distracted. Where possible, create a simplified scenario
(i.e.~minimal, reproducible example {[}4{]}) can be helpful that removes
distractions. The presenter should make sure that the simplified example
works and behaves the way they expect before coming to the Code Club.
Beyond the content, participants should know what they can be expected
to have completed by the end of the session.

@@

Our Code Club needs to fit within an hour slot. The presenter should
anticipate enough time for an introduction and brief instruction, time
for participants to engage the material, and time for everyone to report
back. A typical schedule for Code Review is 10 minutes of introduction
and instruction, 30 minutes of paired programming, 5 minutes to get
groups to wrap up, and 10 minutes to report back to the group. Remember
that a task that you can accomplish in 10 minutes may take a more junior
member of your group 30 minutes. The goal of the Code Club should be to
help that junior member to learn the topic and to reinforce the topic
for the more senior person and help them see the concept in a new
context. One possibility would be to create ``stretch goals'' for those
that complete the task more quickly than everyone else. We once had a
presenter try to teach the group some basic Julia syntax. By the time
people installed the interpreter, the time was up. Alternatively, a
session where participants were asked to make code DRY gave them
multiple stopping points where they could feel successful
(e.g.~commenting code, creating function, implementing function,
refactoring function).

>>>>

It is critical that the presenter and participants respect each other
and that there be an individual (e.g.~the lab director) who enforces a
code of conduct. Everyone in the session needs to have the humility to
acknowledge that they still have more to learn about any topic. We have
found that many problems are avoided when the presenter takes charge of
the session by having a clear lesson plan, thoughtfully creating groups,
and giving encouragement. Similarly, participants foster a positive
environment by remembering that the task is not a competition, focusing
on the presenter's goals, allowing their partner to contribute, asking
clarifying questions when appropriate, and avoiding distractions
(e.g.~email, social media). Learning to program is challenging and too
often it can lead to a toxic environment. All parties in a Code Club are
responsible for preventing this toxicity.

@@

In our early Code Clubs we noticed that if the presenter did not clearly
state their goals for the session, it would often led to frustration for
the presenter and participants. If the presenter shared their own code,
did they want us to focus on their coding style or do they want help
with incorporating a new package into their workflow? Participants will
always notice or ask about things that are not the focus of the
exercise. Be specific about the goal and bring them back to the task if
they are distracted. Where possible, creating a simplified scenario
(i.e.~minimal, reproducible example {[}4{]}) can be helpful to remove
distractions. The presenter should make sure that the simplified example
works and behaves the way they expect before coming to the Code Club.
Beyond the content, participants should know what they can be expected
to have completed by the end of the session.

@@

Our Code Club needs to fit within an hour time slot. The presenter
should anticipate enough time for an introduction and brief instruction,
time for participants to engage the material, and time for everyone to
report back. A typical schedule for Code Review is 10 minutes of
introduction and instruction, 30 minutes of paired programming, 5
minutes to get groups to wrap up, and 10 minutes to report back to the
group. Remember that a task that you can accomplish in 10 minutes may
take a more junior member of your group 30 minutes. The goal of the Code
Club should be to help that junior member to learn the topic and to
reinforce the topic for the more senior person and help them see the
concept in a new context. One possibility would be to create ``stretch
goals'' for those that complete the task more quickly than everyone
else. We once had a presenter try to teach the group some basic Julia
syntax. By the time people installed the interpreter, the time was up.
Alternatively, a session where participants were asked to make code DRY
gave them multiple stopping points where they could feel successful
(e.g.~commenting code, creating function, implementing function,
refactoring function).
